---
title: "LinearModelGenerator"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{LinearModelGenerator}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

First of all, you can using this download command to download this packages and vignettes,
```{r,eval=FALSE}
devtools::install_github('ZihaoHanGitHub/Biostat625_Generate_Linear_Model',build_vignettes =T)
```
Secondly, you can using library to call out this package.
```{r setup}
library(LinearModelGenerator)
library(rbenchmark)
```
\section{Dataset Setup}
In this packages, it contain a dataset about depression, with four variables, Depression, Age, Sex, and Fatalism, it is common to use for a linear regression model calculating, thus, feel good to practice this packages via this dataset.
```{r}
data = LinearModelGenerator::data
head(data)
```
We could see, this data frame contain 612 rows and 4 columns, with four vairables called Depression, Age, Sex and Fatalism, in this tutorial, this dataset is applied for all the example of function using.
\section{Generate Linear Model}
\subsection{How to use this function?}
After we set up the data, we can using the generate linear model with a string (the formula of the model you want to fit), and the dataset, here is the example,
```{r}
# suppose you want to fit the linear model, explore the relationship between Depression with Age, Sex, and Fatalism.
model = generate_linear_model(Depression ~ Age + Sex + Fatalism, data)
```
Thus, you would fit a multiple linear model by Least Squared Estimate, and all the information would save in the variable $model$, in the section of output, it would be introduce how to use this $model$.
\subsection{What is this function output?}
This function would return a list with five things, a mathematics express of this model, a coefficient table, a R squared table, a F-test table, a 95% confident interval of this table, and also a Sum of Sq table.
\subsubsection{The Mathematics Formula & Coefficient Table}
First of all, let's have a overview of this $model$.
```{r}
model
```
Then let's see how to call out each attribute.
```{r}
#Call out the mathematics formula
#it would return a formula type data
math_express = model$Mathematics_formula
math_express
```
Then, let's check the coefficient table
```{r}
# the coefficient table is a dataframe class
# contain these five columns name,
# Estimate: the value of parameter
# Std. Error: the standard error of parameter
# t-value: the t-test value of this parameter
# p-value: the p_value of the t test corresponding.
coefficient_table = model$coefficients_table
coefficient_table
```
And it is easily to call each colunms of coefficient table,
```{r}
# Example:
# using the estimate value
# for other attributes of coefficient table would be similar to call out.
Estimate = coefficient_table[,"Estimate"]
Estimate
```
\subsubsection{}





